Pathogen Spillover - dissertation chapter

### 2016-09-14 pathogen-spillover-diss-ch.Rmd
Add temperature and infection figures.
I also changed the title of the document.

---
title: "Pathogen Spillover - dissertation chapter"
author: "Whalen Dillon"
date: "July 18, 2016"
output:
  html_document:
    self_contained: no
  pdf_document: default
  word_document: default
---

# CHAPTER 3: EFFECTS OF DIVERSITY, TOPOGRAPHY, AND INTERANNUAL CLIMATE VARIABILITY ON PATHOGEN SPILLOVER

@@

## Temperature Figures
```{r temperature figures, echo=F, warning=F, eval=F}
library(ggplot2)
library(scales)
temperatures <- left_join(
      select(summer_temps, plotid, sample_year, hrs_abv25ds),
      select(wet_hrs, plotid, sample_year, hrs1422_wet),
      by = c("plotid","sample_year"))
# oak_sod$year <- as.Date(oak_sod$sample_year)

@@

(sstemps_figure <- temps_figure + 
      geom_boxplot(aes(as.factor(sample_year), hrs_abv25ds)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Number of hours") +
      ggtitle("Dry-season Hours >25 C")
)     
(slc_avg_figure <- temps_figure + 
      geom_boxplot(aes(as.factor(sample_year), avg_lfct)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Symptomatic leaf count") +
      ggtitle("California bay laurel leaf symptoms - plot averages")
)
(slc_total_figure <- temps_figure + 
      geom_boxplot(aes(as.factor(sample_year), tot_lfct)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Symptomatic leaf count") +
      ggtitle("California bay laurel leaf symptoms - plot totals")
)
(rstemps_figure <- temps_figure + 
      geom_boxplot(aes(as.factor(sample_year), hrs1422_wet)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Number of hours") +
      ggtitle("Wet-hours 14-22 C")
)
(oak_infection_figure <- temps_figure +
      geom_bar(aes(as.factor(sample_year), inf_oak_ct), stat = "identity") +
      # geom_boxplot(aes(as.factor(sample_year), inf_oak_ct)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Number of infected oaks") +
      ggtitle("Incident oak infection")
)
```

## Rainfall Figure
Total annual rainfall estimated at plot locations using two-dimensional interpolation methods implemented in GRASS-GIS. The red line indicates the average rainfall from 2005-2014
```{r plot rainfall figure, echo=F}
library(ggplot2)
# summary(rainy_season_ppt)
# rainy_season_ppt$year <- as.factor(rainy_season_ppt$year)
rainfall_figure <- ggplot(filter(rainy_season_ppt, year > 2004), 
                          aes(year, rain2d_total))
rainfall_figure +
      geom_boxplot(aes(group = year)) +
      geom_hline(aes(yintercept = mean(rain2d_total)),
                 colour = "red") +
      xlab("Sample Year") +
      ylab("November-May Total Rainfall (cm)") +
      ggtitle("Rainfall Estimated at Plots from Rain Gauges")
```

>>>>

---
title: "Pathogen Spillover - dissertation chapter"
author: "Whalen Dillon"
date: "July 18, 2016"
output:
  html_document:
    toc: yes
  pdf_document: default
  word_document: default
---

# Appendix 2: Analysis of Environmental Controls on Pathogen Spillover
Effects of Diversity, Topography, and Interannual Climate Variability

@@

## Disease Figures
```{r disease figures, echo=F, warning=F}
library(ggplot2)
temperatures <- left_join(
      select(summer_temps, plotid, sample_year, hrs_abv25ds),
      select(wet_hrs, plotid, sample_year, hrs1422_wet),
      by = c("plotid","sample_year"))
# oak_sod$year <- as.Date(oak_sod$sample_year)
temps_figure <- ggplot(oak_sod, aes(group = sample_year))

(oak_infection_figure <- temps_figure +
      geom_bar(aes(as.factor(sample_year), inf_oak_ct), stat = "identity") +
      # geom_boxplot(aes(as.factor(sample_year), inf_oak_ct)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Number of infected oaks") +
      ggtitle("Oak infection")
)

(slc_avg_figure <- temps_figure + 
      geom_boxplot(aes(as.factor(sample_year), avg_lfct)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Symptomatic leaf count") +
      ggtitle("California bay laurel leaf symptoms - plot averages")
)

(slc_total_figure <- temps_figure + 
      geom_boxplot(aes(as.factor(sample_year), tot_lfct)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Symptomatic leaf count") +
      ggtitle("California bay laurel leaf symptoms - plot totals")
)
```

## Temperature Figures
```{r temperature figures, echo=F, warning=F, eval=T}
library(ggplot2)
library(scales)
temperatures <- left_join(
      select(summer_temps, plotid, sample_year, hrs_abv25ds),
      select(wet_hrs, plotid, sample_year, hrs1422_wet),
      by = c("plotid","sample_year"))
# oak_sod$year <- as.Date(oak_sod$sample_year)

@@

(sstemps_figure <- temps_figure + 
      geom_boxplot(aes(as.factor(sample_year), hrs_abv25ds)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Number of hours") +
      ggtitle("Dry-season Hours >25 C")
)

(rstemps_figure <- temps_figure + 
      geom_boxplot(aes(as.factor(sample_year), hrs1422_wet)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Number of hours") +
      ggtitle("Wet-hours 14-22 C")
)

```

## Rainfall Figure
Total annual rainfall estimated at plot locations using two-dimensional interpolation methods implemented in GRASS-GIS. The red line indicates the average rainfall from 2005-2014.

```{r plot rainfall figure, echo=F}
library(ggplot2)
# summary(rainy_season_ppt)
# rainy_season_ppt$year <- as.factor(rainy_season_ppt$year)
rainfall_figure <- ggplot(filter(rainy_season_ppt, year > 2004), 
                          aes(year, rain2d_total))
rainfall_figure +
      geom_boxplot(aes(group = year)) +
      geom_hline(aes(yintercept = mean(rain2d_total)),
                 colour = "red") +
      theme_bw() +
      xlab("Sample Year") +
      ylab("November-May Total Rainfall (cm)") +
      ggtitle("Rainfall Estimated at Plots from Rain Gauges")
```
